---
title: "Medidas repetidas"
output: html_document
date: "2023-03-17"
---

```{r}
library(lme4)
dat <- rio::import("data/rep_measures.csv")
```

```{r}
dat
```

Random-intercept model, where you have included the cross-level interaction between Treatment and Day (the effect of Day is allowed to vary between Treatment groups)

```{r}
m1 <- lmer(Obs ~ Treatment * Day + (1 | Subject), mydata)
plot(m1)
```

In order to allow for the change over time to differ across participants (i.e. to explicitly model individual differences in change over time), you also need to allow for the effect of Day to be random. To do this, you would specify:

```{r}
m2 <- lmer(Obs ~ Treatment * Day + (1+Day|Subject), mydata)
```


```{r}
# Load necessary packages
library(lme4)
library(lmerTest)
library(car)

# Set up example data
set.seed(123)
ternero <- rep(1:20, each=10)
time <- rep(1:10, times=20)
trt <- rep(rep(1:2, each=5), times=2)
corral <- rep(1:2, each=100)
y <- rnorm(200, mean=5+trt*0.5+corral*1.5+time*0.2+ternero*0.1, sd=1)

# Convert data to data frame
dat <- data.frame(ternero=ternero, time=time, trt=trt, corral=corral, y=y)

# Fit the model using lmer
model <- lmer(y ~ trt*time + (1|ternero) + (1|corral/ternero), data=dat)

# Check assumptions
# Normality of residuals
qqnorm(resid(model))
qqline(resid(model))

# Homogeneity of variance
plot(model, resid(.)~fitted(.))

# Sphericity of residuals
Anova(model, type="III")
summary(model)
```


```{r}
# Load necessary packages
library(tidyverse)
library(lme4)
library(lmerTest)
library(car)

# Load the example dataset
data("PlantGrowth")

# Load the PlantGrowth dataset
data(PlantGrowth)

# Convert data to data frame
one <- PlantGrowth%>% 
  mutate(block=rep(1:10, times=3))
two <- one %>% mutate(weight=weight + abs(1+rnorm(30)))
dat <- bind_rows(list(one, two), .id = "time") %>% 
head(dat)

# Fit the model using lmer
model <- lmer(weight ~ group * time + (1|block/time), data=dat)

# Check assumptions
# Normality of residuals
qqnorm(resid(model))
qqline(resid(model))

# Homogeneity of variance
plot(model, resid(.)~fitted(.))

# Sphericity of residuals
Anova(model, type="III")
```

